---
title: "AntibioticsANOVA"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(papeR)
```

```{r readin,echo=FALSE}
antibiotics <- read.csv('antibiotics.csv', header = TRUE, sep = ",")
```

A student has conducted an experiment evaluating the effect of three different antibiotics --- **ab1**, **ab2**, and **ab3** --- on the growth of *E. coli* in lab cultures.  The results are presented in graphical format below:

```{r chicks, echo=FALSE}
d = ggplot(data = antibiotics)
d + geom_bar(aes(x=as.factor(trt),y=growth),stat="summary",
             fun.y="mean",fill="blue",color="black") + theme_classic() +
            xlab("Treatment")+ylab("Average Growth ")
```

We also include charts summarizing the data: one for the overall dataset, one for each type of treatment, and one for the control.

```{r antisummary,echo=FALSE}
kable(summarize(antibiotics,type='numeric'))
```

```{r ab1 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab1"),],type='numeric'))
```

```{r ab2 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab2"),],type='numeric'))
```

```{r ab3 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab3"),],type='numeric'))
```

```{r control summary, echo=FALSE, results='asis'}
kable(summarize(antibiotics[which(antibiotics$trt=="control"),],type='numeric'))
```

By examining the data, we might expect **ab1** and **ab3** to be significantly different from the control group; **ab2** does not appear significantly different.  Let $\mu_0$ represent the mean of the control, $\mu_1$ represent the mean of **ab1**, $\mu_2$ represent the mean of **ab2**, and $\mu_3$ represent the mean of **ab3**.  Then we have our hypotheses:

**Null Hypothesis $(H_0)$:**  There is not a significant difference in the means of the data: $\mu_0=\mu_1=\mu_2=\mu_3$.

**Alternate Hypothesis $(H_1)$:**  At least one of the antibiotics **ab1**, **ab2**, **ab3** has a mean significantly different from the control group.  That is, for some $i\in\{1,2,3\}$ we have $\mu_i\neq\mu_0$.  

To test these hypotheses we ran an ANOVA-design linear model, and compared the results using a likelihood ratio test.  
