---
title: "AntibioticsANOVA"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(papeR)
```

```{r readin,echo=FALSE}
antibiotics <- read.csv('antibiotics.csv', header = TRUE, sep = ",")
```

A student has conducted an experiment evaluating the effect of three different antibiotics --- **ab1**, **ab2**, and **ab3** --- on the growth of *E. coli* in lab cultures.  The results are presented in graphical format below:

```{r chicks, echo=FALSE}
d = ggplot(data = antibiotics)
d + geom_bar(aes(x=as.factor(trt),y=growth),stat="summary",
             fun.y="mean",fill="blue",color="black") + theme_classic() +
            xlab("Treatment")+ylab("Average Growth ")
```

We also include charts summarizing the data: one for the overall dataset, one for each type of treatment, and one for the control.  Below is the overall summary:

```{r antisummary,echo=FALSE}
kable(summarize(antibiotics,type='numeric'))
```

Below is the summary for **ab1**:

```{r ab1 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab1"),],type='numeric'))
```

Below is the summary for **ab2**:

```{r ab2 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab2"),],type='numeric'))
```

Below is the summary for **ab3**:

```{r ab3 summary, echo=FALSE}
kable(summarize(antibiotics[which(antibiotics$trt=="ab3"),],type='numeric'))
```

Below is the summary for the **control**:

```{r control summary, echo=FALSE, results='asis'}
kable(summarize(antibiotics[which(antibiotics$trt=="control"),],type='numeric'))
```

By examining the data, we might expect **ab1** and **ab3** to be significantly different from the control group; **ab2** does not appear significantly different.  Thus we should expect that our ANOVA will return that the means of at least two groups differ.  Let $\mu_0$ represent the mean growth of the control group, $\mu_1$ represent the mean of the group treated by **ab1**, $\mu_2$ represent the mean of the group treated by **ab2**, and $\mu_3$ represent the mean of the group treated by **ab3**.  Then we have our hypotheses:

**Null Hypothesis $(H_0)$:**  There is not a significant difference in the means of the data: $\mu_0=\mu_1=\mu_2=\mu_3$.

**Alternate Hypothesis $(H_1)$:**  At least one of the antibiotics **ab1**, **ab2**, **ab3** has a mean significantly different from the control group.  That is, for some $i\in\{1,2,3\}$ we have $\mu_i\neq\mu_0$.  

To test these hypotheses we ran an ANOVA-design linear model, and compared the results using a likelihood ratio test. Let $G$ denote growth, let $X_i$ denote treatment by **abi** for $i\in\{1,2,3\}$, and let $\epsilon$ denote a normally distributed error term.  We fit a null model of the form $G=\beta_0$ to this data, optimized for the value of $\beta_0$ which minimized the negative likelihood, and then stored that negative likelihood value.

For our alternate model, we fit a generalized linear model of the form
\[
G=g(X_1,X_2,X_3,)=\beta_0+\beta_1\cdot X_1+\beta_2\cdot X_2+\beta_3\cdot X_3+\epsilon
\]
Note that this is a function $g:\mathbb{R}^3\rightarrow\mathbb{R}$ so we defined our domain as a subset of $\mathbb{R}^3$.  $X_1$ took on the values $(0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0)$, $X_2$ took on the values $(0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0)$, and $X_3$ took on the values $(0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1)$.  The values of $1$ in these vectors correspond to the values of $G=g(X_1,X_2,X_3)$ for which the treatments **ab1**, **ab2**, and **ab3** were affected, respectively.

We optimized the model $g(X_1,X_2,X_3)$ for values of the $\beta_i$ which minimized the negative likelihood and then stored this value.  Then we found $D$, which is twice the difference of our two stored negative likelihood values.  Using a one-tailed $\chi^2$ distribution with $3$ degrees of freedom --- the difference in the amount of parameters between the models --- we found the p-value associated with a $\chi$-score of $D$.  The p-value was approximately $2.97\cdot10^{-8}$.

As the p-value is smaller than $0.05$, we reject the null hypothesis and conclude that there is a significant difference between at least two of the means associated with different treatment types.  
